\documentclass[12pt,a4paper,titlepage]{book}

\usepackage[utf8]{inputenc}
\usepackage[spanish,es-noquoting]{babel}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{lettrine}
\usepackage{float}
\usepackage{color}
\usepackage[top=3cm,bottom=4cm,outer=2cm,inner=2cm]{geometry}
\usepackage{pgf}
\usepackage{emptypage} 
\usepackage{chngcntr}
\usepackage{etoolbox}
\usepackage{listings}
\usepackage{verbatimbox}
\usepackage{rotating} 
\usepackage{tikz}
\usetikzlibrary{arrows}
\usepackage{tkz-graph}
\usepackage{subfig}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{kbordermatrix}

\setlength\parindent{0pt}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
\usepackage[colorlinks=true,linkcolor=black,urlcolor=black,citecolor=black]{hyperref}
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 


\newcommand*{\autores}{
	\begin{tabular}{r}
		Javier Jiménez del Peso\\
	\end{tabular}
}


% Incluye archivo para utilizar el comando \portada
\include{portada}

% Reinicia el contador a 1 en cada parte
%\makeatletter
%\@addtoreset{chapter}{part} 
%\makeatother

\input{comandos}

\begin{document}
	
	\frontmatter
		
	% Portada
	\portada{TFG}{Matemáticas}{Modelos predictivos en rankings}{\autores}{Móstoles}
	% Fin Portada
	
	\tableofcontents
	\listoffigures
	
	
	\mainmatter
	\input{./capitulos/cap1}
	\input{./capitulos/cap2}
	\input{./capitulos/cap3}
	\input{./capitulos/cap4}	
	
	\appendix
	\input{./anexos/grafos}
	\input{./anexos/acb}
	\input{./anexos/matlabcode}
	\input{./anexos/javacode}	
	
	
	\backmatter
	\begin{thebibliography}{X}
		\bibitem{cap1} \textsc{A. N. Langville, C. D. Meyer},
		\textit{Who's \#1? The science of rating and ranking}, 
		Princeton University Press, Princeton, 2012. Chapter 1: \textit{Introduction to Ranking}.
		\bibitem{cap2} \textsc{A. N. Langville, C. D. Meyer},
		\textit{Who's \#1? The science of rating and ranking}, 
		Princeton University Press, Princeton, 2012. Chapter 2: \textit{Massey's Method}.
		\bibitem{cap3} \textsc{A. N. Langville, C. D. Meyer},
		\textit{Who's \#1? The science of rating and ranking}, 
		Princeton University Press, Princeton, 2012. Chapter 3: \textit{Colley's Method}.
		\bibitem{cap4} \textsc{A. N. Langville, C. D. Meyer},
		\textit{Who's \#1? The science of rating and ranking}, 
		Princeton University Press, Princeton, 2012. Chapter 4: \textit{Keener's Method}.
		\bibitem{cap7} \textsc{A. N. Langville, C. D. Meyer},
		\textit{Who's \#1? The science of rating and ranking}, 
		Princeton University Press, Princeton, 2012. Chapter 7: \textit{The Offense-Defense Rating Method}.		
		\bibitem{otros_met} \textsc{A. N. Langville, C. D. Meyer},
		\textit{Who's \#1? The science of rating and ranking}, 
		Princeton University Press, Princeton, 2012. Chapters 5, 6 \& 8.			
		\bibitem{perron} \textsc{C.D. Meyer},
		\textit{Matrix analysis and applied linear algebra}, 
		SIAM, Philadelphia, 2000. Chapter 8: \textit{Perron-Frobenius Theory}.	
		\bibitem{power_method}
		Artículo sobre el método de la potencia en Wikipedia (Inglés). \url{https://en.wikipedia.org/wiki/Power_iteration}
		\bibitem{cap13-14} \textsc{A. N. Langville, C. D. Meyer},
		\textit{Who's \#1? The science of rating and ranking}, 
		Princeton University Press, Princeton, 2012. Chapters 14 \& 15: \textit{Rank Aggregation parts 1 \& 2}.
		\bibitem{refborda} \textsc{E. B. Burger, M. Starbird},
		\textit{The Heart of Mathematics. An invitation to effective thinking}, 
		Third Edition, John Wiley \& Sons, 2010. Chapter Nine: \textit{Deciding wisely}.		
		\bibitem{refbilp} \textsc{K. E. Pedings, A. N. Langville, Yoshitsugu Yamamoto},
		\textit{A Minimum Violations Ranking Method}, 
		2009. Chapter 4: \textit{Theorem for the Relationship between the BILP and LP}.
		\bibitem{cap16} \textsc{A. N. Langville, C. D. Meyer},
		\textit{Who's \#1? The science of rating and ranking}, 
		Princeton University Press, Princeton, 2012. Chapter 16: \textit{Methods of Comparison}.
		\bibitem{refcomp} \textsc{R. Criado, E. García, F. Pedroche, M. Romance},
		\textit{On graphs associated to sets of rankings}, 
		2014. Chapter 2: \textit{Competitivity graphs}.
		\bibitem{refpred1} \textsc{M. Spann, B. Skiera},
		\textit{Sports forecasting: A comparison of the forecast accuracy of prediction markets, betting odds and tipsters}, 
		John Wiley \& Sons, Ltd. 2008. 
		\bibitem{refpred2} \textsc{T. Cheng, D. Cui, Z. Fan, J. Zhou, S. Lu},
		\textit{A new model to forecast the results of matches based on hybrid neural networks in the soccer rating system}, 
		2003. 
		\bibitem{refpred3} \textsc{G. Hiranandani, J. Shitole, N. Kundu, N. Maurya, R. Grover},
		\textit{Forecasting Indian Premier League Results Using Time Series Analysis}, 
		2013. 	
		\bibitem{refpuentes}
		Artículo sobre el problema de los puentes de Königsberg en Wikipedia (Castellano). \url{https://es.wikipedia.org/wiki/Problema_de_los_puentes_de_Konigsberg}
		\bibitem{librografos} \textsc{W. Kocay, D.L. Kreher},
		\textit{Graphs, algorithms, and optimization}, 
		Chapman and Hall/CRC, 2004.
	\end{thebibliography}

	
	
\end{document}